---
title: "Plotting"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Plotting}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=FALSE}
library(sententia)
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyquant)
```

Lets plot the latest sentiment index using `sent_index()` function. 

In this example we will be calling the `economic` focus index that is constructed using news data from Business Day. To characterize the sentiment, we use the `Loughran` dictionary and calculate the sentiment *within* each article using the `logit` formulation.

```{r}
msi_data <- sent_index(
   source = "all",
   topic = "global",
   freq = "month",
   dict = "loughran",
   aggr = "sent_logit"
   )

```

Once we have retrieved it is fairly easy to plot the index and the different `time` aggregations using `ggplot2`.

```{r, fig.width=12}
msi_data %>% 
  filter(published_date > "2003-01-01") %>% 
  mutate(published_date = as.Date(published_date)) %>% 
  pivot_longer(names_to = "sentiment_type", values_to = "values", -c(source:aggr_type)) %>% 
  ggplot(., aes(published_date, values, group = sentiment_type), color = 1) +
  geom_line(color = "#BC4744") +
  geom_ma(color = "#18417B", n = 3, linetype = "solid", ma_fun = EMA) +
  labs(title = "Media Sentiment BER: Economic Focus", 
       subtitle = "Loughran (sent logit)",
       y = "Index", 
       x = "Date", 
       caption = "(Business Day)") + 
  scale_x_date() +
  facet_wrap(~sentiment_type, scales = "free_y") +
  theme_tq()
```

